A Closed-Form Solution to the Doppler Imaging Problem

### 2021-09-08 src/ms.tex
new structure

% Define document class & import showyourwork
\documentclass[modern]{aastex631}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{kT.pdf}
        \caption{%
            The Doppler $\kT$ basis for a rigidly rotating star computed from Equation~(\ref{eq:kT:kT}) and Equation~(\ref{eq:kT:sTrecurrence}) up to spherical harmonic degree $l_\mathrm{max}=10$. 
            Rows correspond to the degree $l$ and columns correspond to the order $m$. 
            These functions encode the contribution of each spherical harmonic to the rotational broadening of features in the stellar spectrum. 
            Because the rotational axis is chosen to be aligned with $\hat{y}$, none of the $m < 0$ harmonics contribute to the observed spectrum.
        }
        \label{fig:kT}
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.6\linewidth]{spot.pdf}
        \caption{%
            Time evolution of a Gaussian absorption line on a rigidly rotating, spotted star computed from the analytic formulae in \S\ref{sec:kT}.
            The stellar surface is modeled as a spherical harmonic expansion up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
            the spot simply downweights the local intensity at all wavelengths.
            As the spot rotates into view (left panel), the line shape changes slightly (center panel). 
            The residuals between the line when the spot is in view (solid) and when it is on the backside of the star (dotted) are shown in the right panel, where a Gaussian-like feature can be seen tracking the spot as it rotates from the blueshifted hemisphere to the redshifted hemisphere of the star.
        }
        \label{fig:spot}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.65\linewidth]{compare.pdf}
        \caption{%
            The observed spectrum when the spot is in view computed with
            \starry (blue) and numerically (orange). 
            The problem setup is the same as that in Figure~\ref{fig:spot}. 
            The boottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
            As the number of grid points increases, the numerical solution approaches the \starry solution.
        }
        \label{fig:compare}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{linalg.pdf}
        \caption{%
            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), constructed from a grid of Toeplitz matrices, each of shape $K \times K'$, where $K$ is the number of wavelength bins in the observed spectrum and $K' = K + W - 1$ is the number of bins in the model spectrum, where $W$ is the width of the convolution kernel.
            The $N$ columns of $\Doppler$ correspond to the Toeplitz matrices for each of the $N$ spherical harmonics (shown at the top);
            the $M$ rows correspond to the Toeplitz matrices rotated to each of the $M$ stellar phases observed (indicated graphically to the left of $\Doppler$).
        }
        \label{fig:linalg}
    \end{centering}
\end{figure}

@@

\subsection{Limb darkening}
\label{sec:ld}
%
Thus far we have avoided mention of limb darkening, whose effect on the observed spectrum can often be significant. 
A proper treatment of limb darkening requires solution of radiative transfer equations and should account for the temperature and composition gradients in the stellar atmosphere. 
However, in the spirit of data-driven inference, we can approximate the effect of limb darkening by weighting the spatial component of our map by the limb darkening profile of the star, which can either be imposed or learned from the data. 
For a polynomial limb darkening law of the form
%
\begin{align}
    \label{eq:ld:I}
    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
    \quad,
\end{align}
%
where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the projected disk and $u_n$ is a limb darkening coefficient, the effect of limb darkening on the stellar map can be expressed exactly as a linear operation on the spherical harmonic coefficient vector \citep{Luger2019,Agol2019}. 
This can be understood by noting that all terms in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$, all of which can be expressed exactly as sums of spherical harmonics \citep{Luger2019}. 
When weighting the surface intensity by the limb darkening profile, the resulting intensity is simply a product of spherical harmonics, which is itself a sum of spherical harmonics. 
Given a limb darkening law of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$ that transforms a spherical harmonic vector $\bvec{y}$ of degree $l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$ of degree $l_\mathrm{max} + n_\mathrm{max}$. 
As an example, consider a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law ($n_\mathrm{max} = 1$).
The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
%
\begin{align}
    \label{eq:ld:L}
    \bvec{L} =
    \frac{1}{1 - \frac{u_1}{3}}
    \begin{pmatrix}
        \quadquad1-u_1\quadquad & 0                       & \frac{u_1}{\sqrt{3}}    & 0                       \\
        0                       & \quadquad1-u_1\quadquad & 0                       & 0                       \\
        \frac{u_1}{\sqrt{3}}    & 0                       & \quadquad1-u_1\quadquad & 0                       \\
        0                       & 0                       & 0                       & \quadquad1-u_1\quadquad \\
        0                       & 0                       & 0                       & 0                       \\
        0                       & \frac{u_1}{\sqrt{5}}    & 0                       & 0                       \\
        0                       & 0                       & \frac{2u_1}{\sqrt{15}}  & 0                       \\
        0                       & 0                       & 0                       & \frac{u_1}{\sqrt{5}}    \\
        0                       & 0                       & 0                       & 0
    \end{pmatrix}
    \quad.
\end{align}
%
The columns of $\bvec{L}$ are constructed from the coefficient vectors of each transformed spherical harmonic, which are in turn computed by multiplying each spherical harmonic by the spherical harmonic decomposition of the particular limb darkening law.
Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each of the first four spherical harmonics.
%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{ld.pdf}
        \caption{%
            Illustration of the limb darkening transformation given by Equation~(\ref{eq:ld:L}) for a linear limb darkening law with $u_1 = 1$. 
            Each row shows a spherical harmonic before (left) and after (right) transformation by $\bvec{L}$.
        }
        \label{fig:ld}
    \end{centering}
\end{figure}
%

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{spot_setup.pdf}
        \caption{%
            The basic setup for the \spot problem. 
            We compute the $l_\mathrm{max} = 15$ spherical harmonic expansion of a map where the word ``SPOT'' has been placed across the northern hemisphere (top left). 
            Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close ot unity outside the spot (point labeled \texttt{A}).
            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).
            The grey regions indicate wavelength regions outside the observation window, but whose features still contribute to the observed spectrum due to rotational broadening.
        }
        \label{fig:spot_setup}
    \end{centering}
\end{figure}

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{spot_y1_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{spot_y1_rect.pdf}
%         \caption{%
%             The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
%             The panel on the left shows the inferred map at each of the 16
%             epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
%             The rectangular projection of the original map is shown at the top right; the inferred map is displayed below it. 
%             The bottom panel shows the posterior uncertainty as a function of latitude and longitude, ranging from close to zero in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$ below a latitude of $-30^\circ$. 
%             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
%         }
%         \label{fig:spot_y1}
%     \end{centering}
% \end{figure}

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{spot_y1b_timeseries.pdf.pdf}
%         \includegraphics[width=0.49\linewidth]{spot_y1b_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{spot_y1b_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{spot_y1b_coeffs.pdf}
%         \caption{%
%             Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline is not known. 
%             The panel at the bottom left shows the true baseline (blue) and the inferred baseline (orange), along with its $1\sigma$ uncertainty. 
%             The large offset between the two highlights one of the fundamental degeneracies of the problem: since most of the southern hemisphere of the star is never visible, the coefficient of the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic is not constrained by the data, resulting in an unknowable additive offset in the baseline.
%             This effect can be seen also in (\emph{a}) the inferred map, where the background intensity in the northern hemisphere is significantly larger than that in the southern hemisphere, and (\emph{b}) the spherical harmonic coefficients (bottom right), where a large discrepancy is visible between the true and inferred values of the first two coefficients.
%         }
%         \label{fig:spot_y1b}
%     \end{centering}
% \end{figure}

Our results are shown in Figure~\ref{fig:spot_y1b}. 
The panels at the top are the same as those in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline (lower left) and spherical harmonic coefficients (lower right) next to the true values. 
We recover the \texttt{SPOT} map just as well as before, except for the presence of a strong dipolar artifact; the background intensity level is higher in the northern hemisphere and lower in the southern hemisphere. 
This effect is closely related to the fact that we do not know the true baseline. 
While we are able to infer the shape of the baseline exceedingly well (lower left panel), there is a large offset between the true value and our inferred value. 
This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data. 
The magnitude of the true value of the coefficient is quite large (lower right panel), since the northern hemisphere \emph{is} significantly darker than the southern hemisphere; however, the data do not constrain this, and our prior shrinks all coefficients toward zero. 
The net effect is that the region surrounding the spot in the northern hemisphere gets brighter to even out the difference between the two hemispheres. 
This causes the visible portion of the star to get brighter, raising the baseline relative to the true value.

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{spot_y1bs_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{spot_y1bs_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{spot_y1bs_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{spot_y1bs_coeffs.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.98\linewidth]{spot_y1bs_spectrum.pdf}
%         \caption{%
%             Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
%             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
%         }
%         \label{fig:spot_y1bs}
%     \end{centering}
% \end{figure}

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{spot_y1bs_low_snr_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{spot_y1bs_low_snr_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{spot_y1bs_low_snr_coeffs.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.98\linewidth]{spot_y1bs_low_snr_spectrum.pdf}
%         \caption{%
%             Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
%             We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
%         }
%         \label{fig:spot_y1bs_low_snr}
%     \end{centering}
% \end{figure}

Because the problem is generally not convex, we need a good starting guess for either the spectrum or the map coefficients. 
We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}).
In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
Given this starting value of $\bvec{s}$, we compute an initial guess for $\bvec{y_1}$ using the linear baseline approximation. 
We then iterate between solving for $\bvec{s}$ and solving for $\bvec{y_1}$, always using the previous value of the baseline to compute $\bvec{y_1}$. 
As in the previous section, we find it necessary to implement a tempering scheme, except with a much higher starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
We again refine our solution with \texttt{NAdam}, this time setting $N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. 
Since we are now solving for the spectrum as well, we include the negative log prior term for the spectrum, $\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$, in Equation~(\ref{eq:spotstar:logP}).

@@

% \begin{figure}[t!]
%     \begin{centering}
%         \includegraphics[width=\linewidth]{twospec.pdf}
%         \caption{%
%             An example of a star whose spectrum is different within the spot (\texttt{B}) and outside of the spot (\texttt{A}). 
%             Everywhere on the surface, the spectrum is a linear combination of two spectral components ($s_1$ and $s_2$).
%             As in Figure~\ref{fig:spot_y1bs}, we assume we do not know the map, the baseline, or either of the spectra.
%             The top row shows the true values for the map and the spectra, and the bottom row shows our inferred values. 
%         }
%         \label{fig:twospec}
%     \end{centering}
% \end{figure}

@@

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
We recover the \spot feature reasonably well, although with more artifacts than in the previous experiments. 
We also recover the two spectral components, although our solution for $\bvec{s_2}$ is significantly better than that for $\bvec{s_1}$. 
This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{kT00.pdf}}), since this spectral component has no spatial variability.
Since the deconvolution operation is in general ill-posed, there is no unique solution for $\bvec{s_1}$. 
On the other hand, the other spectral component projects into the data via convolutions with all other terms of the kernel and is therefore very well constrained.
Finally, we can estimate the spectra at points \texttt{A} and \texttt{B} as before (center panel). 
We recover the single spectral line at \texttt{A} and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty in $\bvec{s_1}$.

@@

As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 100 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
Interestingly, south of the equator, the map quality actually begins to degrade with higher SNR. 
This is due to the fact that finding the global optimum becomes exponentially more difficult with higher SNR, as the posterior volume becomes ever smaller. 
Even with aggressive tempering, we were unable to converge on the best solution for SNR $\gtrsim 500$ given our standard, conservative priors and initial guesses (\S\ref{sec:spotstar}).
%
% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.98\linewidth]{snr.pdf}
%         \caption{%
%             Recovered \spot map as a function of SNR per resolution element.
%             The quality of the inferred map in the northern hemisphere improves with SNR, but at very high SNR the region surrounding the global optimum becomes so small that our optimization methods struggle to converge on the correct solution.
%         }
%         \label{fig:snr}
%     \end{centering}
% \end{figure}

>>>>

% Define document class
\documentclass[modern]{aastex631}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/kT.pdf}
        \caption{%
            The Doppler $\kT$ basis for a rigidly rotating star computed from Equation~(\ref{eq:kT:kT}) and Equation~(\ref{eq:kT:sTrecurrence}) up to spherical harmonic degree $l_\mathrm{max}=10$. 
            Rows correspond to the degree $l$ and columns correspond to the order $m$. 
            These functions encode the contribution of each spherical harmonic to the rotational broadening of features in the stellar spectrum. 
            Because the rotational axis is chosen to be aligned with $\hat{y}$, none of the $m < 0$ harmonics contribute to the observed spectrum.
        }
        \label{fig:kT}
    \end{centering}
\end{figure}

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.6\linewidth]{figures/spot.pdf}
        \caption{%
            Time evolution of a Gaussian absorption line on a rigidly rotating, spotted star computed from the analytic formulae in \S\ref{sec:kT}.
            The stellar surface is modeled as a spherical harmonic expansion up to $l_\mathrm{max}=20$, and the line shape is assumed to be the same everywhere;
            the spot simply downweights the local intensity at all wavelengths.
            As the spot rotates into view (left panel), the line shape changes slightly (center panel). 
            The residuals between the line when the spot is in view (solid) and when it is on the backside of the star (dotted) are shown in the right panel, where a Gaussian-like feature can be seen tracking the spot as it rotates from the blueshifted hemisphere to the redshifted hemisphere of the star.
        }
        \label{fig:spot}
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.65\linewidth]{figures/compare.pdf}
        \caption{%
            The observed spectrum when the spot is in view computed with
            \starry (blue) and numerically (orange). 
            The problem setup is the same as that in Figure~\ref{fig:spot}. 
            The boottom panel shows the absolute value of the difference between the two spectra for different number of grid points in the numerical solution.
            As the number of grid points increases, the numerical solution approaches the \starry solution.
        }
        \label{fig:compare}
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.8\linewidth]{figures/linalg.pdf}
        \caption{%
            The Doppler design matrix $\Doppler$ (Equation~\ref{eq:linear:f}), constructed from a grid of Toeplitz matrices, each of shape $K \times K'$, where $K$ is the number of wavelength bins in the observed spectrum and $K' = K + W - 1$ is the number of bins in the model spectrum, where $W$ is the width of the convolution kernel.
            The $N$ columns of $\Doppler$ correspond to the Toeplitz matrices for each of the $N$ spherical harmonics (shown at the top);
            the $M$ rows correspond to the Toeplitz matrices rotated to each of the $M$ stellar phases observed (indicated graphically to the left of $\Doppler$).
        }
        \label{fig:linalg}
    \end{centering}
\end{figure}

@@

\subsection{Limb darkening}
\label{sec:ld}
%
Thus far we have avoided mention of limb darkening, whose effect on the observed spectrum can often be significant. 
A proper treatment of limb darkening requires solution of radiative transfer equations and should account for the temperature and composition gradients in the stellar atmosphere. 
However, in the spirit of data-driven inference, we can approximate the effect of limb darkening by weighting the spatial component of our map by the limb darkening profile of the star, which can either be imposed or learned from the data. 
For a polynomial limb darkening law of the form
%
\begin{align}
    \label{eq:ld:I}
    \frac{I(\mu)}{I(\mu = 1)} = 1 - \sum_{n=1}^{n_\mathrm{max}} u_n(1 - \mu)^n
    \quad,
\end{align}
%
where $\mu = z = \sqrt{1 - x^2 - y^2}$ is the radial coordinate on the projected disk and $u_n$ is a limb darkening coefficient, the effect of limb darkening on the stellar map can be expressed exactly as a linear operation on the spherical harmonic coefficient vector \citep{Luger2019,Agol2019}. 
This can be understood by noting that all terms in Equation~(\ref{eq:ld:I}) are strictly polynomials in $x$, $y$, and $z$, all of which can be expressed exactly as sums of spherical harmonics \citep{Luger2019}. 
When weighting the surface intensity by the limb darkening profile, the resulting intensity is simply a product of spherical harmonics, which is itself a sum of spherical harmonics. 
Given a limb darkening law of degree $n_\mathrm{max}$, we can always construct a matrix $\bvec{L}$ that transforms a spherical harmonic vector $\bvec{y}$ of degree $l_\mathrm{max}$ to a limb-darkened spherical harmonic vector $\bvec{y'}$ of degree $l_\mathrm{max} + n_\mathrm{max}$. 
As an example, consider a map of degree $l_\mathrm{max} = 1$ and the linear limb darkening law ($n_\mathrm{max} = 1$).
The transformation matrix from $\bvec{y}$ to $\bvec{y'}$ is
%
\begin{align}
    \label{eq:ld:L}
    \bvec{L} =
    \frac{1}{1 - \frac{u_1}{3}}
    \begin{pmatrix}
        \quadquad1-u_1\quadquad & 0                       & \frac{u_1}{\sqrt{3}}    & 0                       \\
        0                       & \quadquad1-u_1\quadquad & 0                       & 0                       \\
        \frac{u_1}{\sqrt{3}}    & 0                       & \quadquad1-u_1\quadquad & 0                       \\
        0                       & 0                       & 0                       & \quadquad1-u_1\quadquad \\
        0                       & 0                       & 0                       & 0                       \\
        0                       & \frac{u_1}{\sqrt{5}}    & 0                       & 0                       \\
        0                       & 0                       & \frac{2u_1}{\sqrt{15}}  & 0                       \\
        0                       & 0                       & 0                       & \frac{u_1}{\sqrt{5}}    \\
        0                       & 0                       & 0                       & 0
    \end{pmatrix}
    \quad.
\end{align}
%
The columns of $\bvec{L}$ are constructed from the coefficient vectors of each transformed spherical harmonic, which are in turn computed by multiplying each spherical harmonic by the spherical harmonic decomposition of the particular limb darkening law.
Figure~\ref{fig:ld} shows this transformation with $u_1 = 1$ applied to each of the first four spherical harmonics.
%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/ld.pdf}
        \caption{%
            Illustration of the limb darkening transformation given by Equation~(\ref{eq:ld:L}) for a linear limb darkening law with $u_1 = 1$. 
            Each row shows a spherical harmonic before (left) and after (right) transformation by $\bvec{L}$.
        }
        \label{fig:ld}
    \end{centering}
\end{figure}
%

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/spot_setup.pdf}
        \caption{%
            The basic setup for the \spot problem. 
            We compute the $l_\mathrm{max} = 15$ spherical harmonic expansion of a map where the word ``SPOT'' has been placed across the northern hemisphere (top left). 
            Each point on the surface is given the same spectrum, composed of a sum of synthetic Gaussian absorption lines (blue curve in the bottom panel).
            The specific intensity at each point on the surface is equal to this spectrum weighted by the intensity of the map, which is close to zero within the spot (point labeled \texttt{B}) and close ot unity outside the spot (point labeled \texttt{A}).
            To generate the synthetic dataset (orange curves in the bottom panel), the star is inclined at $40^\circ$ with respect to the line of sight and the disk-integrated spectrum is computed at 16 equally-spaced phases between $-180^\circ$ and $180^\circ$ (middle panel).
            The grey regions indicate wavelength regions outside the observation window, but whose features still contribute to the observed spectrum due to rotational broadening.
        }
        \label{fig:spot_setup}
    \end{centering}
\end{figure}

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1_rect.pdf}
%         \caption{%
%             The solution to the \spot problem at high SNR when both the rest frame spectrum and the baseline are known.
%             The panel on the left shows the inferred map at each of the 16
%             epochs, alongside the observed spectrum (black points) and the best-fit model (orange lines). 
%             The rectangular projection of the original map is shown at the top right; the inferred map is displayed below it. 
%             The bottom panel shows the posterior uncertainty as a function of latitude and longitude, ranging from close to zero in the northern hemisphere to $\sigma_\mathrm{prior} \approx 10\%$ below a latitude of $-30^\circ$. 
%             The latter is the uncertainty associated with our particular choice of prior, as the southernmost latitudes of the star are never visible to the observer.
%         }
%         \label{fig:spot_y1}
%     \end{centering}
% \end{figure}

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_timeseries.pdf.pdf}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1b_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{figures/spot_y1b_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{figures/spot_y1b_coeffs.pdf}
%         \caption{%
%             Similar to Figure~\ref{fig:spot_y1}, but assuming the baseline is not known. 
%             The panel at the bottom left shows the true baseline (blue) and the inferred baseline (orange), along with its $1\sigma$ uncertainty. 
%             The large offset between the two highlights one of the fundamental degeneracies of the problem: since most of the southern hemisphere of the star is never visible, the coefficient of the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{Y1m1.pdf}}) spherical harmonic is not constrained by the data, resulting in an unknowable additive offset in the baseline.
%             This effect can be seen also in (\emph{a}) the inferred map, where the background intensity in the northern hemisphere is significantly larger than that in the southern hemisphere, and (\emph{b}) the spherical harmonic coefficients (bottom right), where a large discrepancy is visible between the true and inferred values of the first two coefficients.
%         }
%         \label{fig:spot_y1b}
%     \end{centering}
% \end{figure}

Our results are shown in Figure~\ref{fig:spot_y1b}. 
The panels at the top are the same as those in Figure~\ref{fig:spot_y1}, but now we also plot the inferred baseline (lower left) and spherical harmonic coefficients (lower right) next to the true values. 
We recover the \texttt{SPOT} map just as well as before, except for the presence of a strong dipolar artifact; the background intensity level is higher in the northern hemisphere and lower in the southern hemisphere. 
This effect is closely related to the fact that we do not know the true baseline. 
While we are able to infer the shape of the baseline exceedingly well (lower left panel), there is a large offset between the true value and our inferred value. 
This is due to a fundamental degeneracy involving the $Y_{1,-1}$ (\raisebox{-0.2em}{\includegraphics[width=1em]{figures/Y1m1.pdf}}) spherical harmonic coefficient, which, because a large portion of the southern hemisphere is never in view, cannot be constrained by the data. 
The magnitude of the true value of the coefficient is quite large (lower right panel), since the northern hemisphere \emph{is} significantly darker than the southern hemisphere; however, the data do not constrain this, and our prior shrinks all coefficients toward zero. 
The net effect is that the region surrounding the spot in the northern hemisphere gets brighter to even out the difference between the two hemispheres. 
This causes the visible portion of the star to get brighter, raising the baseline relative to the true value.

@@

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_coeffs.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_spectrum.pdf}
%         \caption{%
%             Similar to Figure~\ref{fig:spot_y1}, but assuming we have no information about either the spectrum, the baseline, or the map coefficients. 
%             The bottommost panel now shows the true rest frame spectrum (blue line), the initial guess based on a deconvolution (dashed orange line), and the inferred spectrum (orange line, with shaded $1\sigma$ uncertainty).
%         }
%         \label{fig:spot_y1bs}
%     \end{centering}
% \end{figure}

% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_timeseries.pdf}
%         \includegraphics[width=0.49\linewidth]{figures/spot_y1bs_low_snr_rect.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.405\linewidth]{figures/spot_y1bs_low_snr_baseline.pdf}
%         \includegraphics[width=0.575\linewidth]{figures/spot_y1bs_low_snr_coeffs.pdf}
%         \\[0.5em]
%         \includegraphics[width=0.98\linewidth]{figures/spot_y1bs_low_snr_spectrum.pdf}
%         \caption{%
%             Same as Figure~\ref{fig:spot_y1bs}, but for $10\times$ lower SNR.
%             We still recover the \spot map and the input spectrum, albeit with higher uncertainty, as expected.
%         }
%         \label{fig:spot_y1bs_low_snr}
%     \end{centering}
% \end{figure}

Because the problem is generally not convex, we need a good starting guess for either the spectrum or the map coefficients. 
We note that we can very crudely approximate the rest frame spectrum by deconvolving the average observed spectrum with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}).
In practice, this is a fairly poor approximation, but we find that it suffices as an initial guess. 
Given this starting value of $\bvec{s}$, we compute an initial guess for $\bvec{y_1}$ using the linear baseline approximation. 
We then iterate between solving for $\bvec{s}$ and solving for $\bvec{y_1}$, always using the previous value of the baseline to compute $\bvec{y_1}$. 
As in the previous section, we find it necessary to implement a tempering scheme, except with a much higher starting temperature $T_0 = 5,000$ and a slower decay $\Delta\log T = -0.04$.
We again refine our solution with \texttt{NAdam}, this time setting $N_\mathrm{nadam} = 3,000$ and $L_\mathrm{nadam} = 2.5\times 10^{-5}$. 
Since we are now solving for the spectrum as well, we include the negative log prior term for the spectrum, $\frac{1}{2}(\bvec{s - 1})^\top \boldsymbol{\Lambda}_\bvec{s}^{-1}(\bvec{s - 1})$, in Equation~(\ref{eq:spotstar:logP}).

@@

% \begin{figure}[t!]
%     \begin{centering}
%         \includegraphics[width=\linewidth]{figures/twospec.pdf}
%         \caption{%
%             An example of a star whose spectrum is different within the spot (\texttt{B}) and outside of the spot (\texttt{A}). 
%             Everywhere on the surface, the spectrum is a linear combination of two spectral components ($s_1$ and $s_2$).
%             As in Figure~\ref{fig:spot_y1bs}, we assume we do not know the map, the baseline, or either of the spectra.
%             The top row shows the true values for the map and the spectra, and the bottom row shows our inferred values. 
%         }
%         \label{fig:twospec}
%     \end{centering}
% \end{figure}

@@

The results are shown in the bottom panel of Figure~\ref{fig:twospec}.
We recover the \spot feature reasonably well, although with more artifacts than in the previous experiments. 
We also recover the two spectral components, although our solution for $\bvec{s_2}$ is significantly better than that for $\bvec{s_1}$. 
This is due to the fact that the only information about $\bvec{s_1}$ that makes it into our dataset is the convolution of $\bvec{s_1}$ with the first term of the convolution kernel $\kT$ (\raisebox{-0.1em}{\includegraphics[width=2em]{figures/kT00.pdf}}), since this spectral component has no spatial variability.
Since the deconvolution operation is in general ill-posed, there is no unique solution for $\bvec{s_1}$. 
On the other hand, the other spectral component projects into the data via convolutions with all other terms of the kernel and is therefore very well constrained.
Finally, we can estimate the spectra at points \texttt{A} and \texttt{B} as before (center panel). 
We recover the single spectral line at \texttt{A} and the two lines at \texttt{B}, albeit rather noisily due to the uncertainty in $\bvec{s_1}$.

@@

As the SNR incraeses, however, the quality of the \spot feature does not improve appreciably, since a SNR of 100 is more than sufficient to recover a $l_\mathrm{max} = 15$ band-limited map. 
Interestingly, south of the equator, the map quality actually begins to degrade with higher SNR. 
This is due to the fact that finding the global optimum becomes exponentially more difficult with higher SNR, as the posterior volume becomes ever smaller. 
Even with aggressive tempering, we were unable to converge on the best solution for SNR $\gtrsim 500$ given our standard, conservative priors and initial guesses (\S\ref{sec:spotstar}).
%
% \begin{figure}[p!]
%     \begin{centering}
%         \includegraphics[width=0.98\linewidth]{figures/snr.pdf}
%         \caption{%
%             Recovered \spot map as a function of SNR per resolution element.
%             The quality of the inferred map in the northern hemisphere improves with SNR, but at very high SNR the region surrounding the global optimum becomes so small that our optimization methods struggle to converge on the correct solution.
%         }
%         \label{fig:snr}
%     \end{centering}
% \end{figure}
